---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ggformulaExtra

ggformulaExtra provides some addiitonal functionality to ggformula.  Typically, this functionality either

 * relies on additional packages beyond ggplot2, or
 
 * is "experimental"


## Installation

You can install ggformulaExtra from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ProjectMOSAIC/ggformulaExtra")
```

## Example

This is a basic example that uses `ggrepel` to solve a common problem -- text labels that
overlap.

```{r example}
library(ggformulaExtra)
theme_set(theme_bw())

mtcars$model <- rownames(mtcars)
mtcars$cylinders <- factor(mtcars$cyl)

p <-
  gf_point(mpg ~ wt, data = mtcars, color = ~ cylinders)

# Avoid overlaps by repelling text labels
p %>% gf_text_repel(label = ~ model)

# Labels with background
p %>% gf_label_repel(label = ~ model)

# Add aesthetic mappings
p %>% gf_text_repel(alpha = ~ wt, size = ~ mpg, label = ~ model)
p %>% gf_label_repel(label = ~ model,
                     fill = ~ factor(cyl), color = "white", segment.color = "black")
```

More examples can be found in the package documentation.
